---
title: Rmarkdown
author: Akhilesh Atluri
date: '2017-09-15'
slug: rmarkdown
categories: [R]
tags: [dplyr,Lahman,Baseball,Datascience]
description: ''
thumbnail: ''
---

## The packages required to run the code

```{r message =FALSE, warning=FALSE}
library(Lahman)
library(dplyr)
```

## Selecting a particular Column in the dataframe
now , suppose we would like to see the homerun totals for the 1927 new york yankees. we could run the following code

```{r}

Batting%>%
  select(playerID,yearID,teamID,HR)%>%
filter(teamID=="NYA" & yearID==1927)

```

## Arranging a Column in Descending Order

Now,the following code gives the list of all the players that have scored more than 40 homeruns from New York Yankees Team.

```{r}
Batting%>%
  select(playerID,yearID,teamID,HR,SO,AB)%>%
  filter(teamID == "NYA" & HR > 40)%>%
  arrange(desc(HR))
```

Next let's find all the players from the data who has scored over 40 homeruns but have less than 60 strikeouts.

## F iltering rows depending on the statistics

```{r}
Batting%>%
  select(playerID,yearID,teamID,HR,SO)%>%
  filter(SO < 60 ,HR >= 40)%>%
  arrange(desc(HR))
```

If we want to see players with more than 30 homeruns scored from Phillies in 1970's we can use the following code.

```{r}
Batting%>%
  select(playerID,yearID,teamID,HR,SO,AB)%>%
  filter(teamID == "PHI" & HR > 30 & yearID >=1970 & yearID <= 1979)%>%
  arrange(desc(HR))